### 2016-10-26 thesis/intro/intro.tex
tmp commit

@@

Until these terrible trends stop, and even after the trend stops, the world will need a plan to live along with this ongoing global epidemic of obesity and its associated diseases.

@@

% \subsection{Preventive measure of obesity}
% \label{sub:preventive_measure_of_obesity}

>>>>

\citep{Gelber2008, Lee2008, Yusuf2005}

@@

Until these terrible trends stop, and even after the trends stop, the world will need a plan to live along with this ongoing global epidemic of obesity and its associated diseases.

\subsection{Causes of Obesity}
\label{sub:causes_of_obesity}

\citep{Malik2013}

@@

\citep{Malik2013, Franks2010}

\subsection{Preventive measure of obesity}
\label{sub:preventive_measure_of_obesity}

\citep{Malik2013}
